Bayesian Insights into Aerial Bombing Strategies: An Ordered Logistic Regression Analysis of WWII Target Prioritization Against Germany

### 2024-04-17 paper/paper.qmd
modify model and add some graph in qmd

library(arrow)
library(knitr)
library(modelsummary)
library(rstanarm)
library(tidyverse)
library(ggplot2)
library(bayesplot)
```

@@

# Load in data
# ces2022_1 <- read_csv("data/cleaned_ces2022_1.csv")
# ces2022_2 <- read_csv("data/cleaned_ces2022_2.csv")
# 
# ces2022_1 |>
#   head() |>
#   kable(
#     col.names = c("Voted For (2020)", "Age Group", "Gender", "Education", "Race", "Religion"),
#     booktabs = TRUE
  # )
```

@@

# library(rstanarm)
# 
# first_model <-
#   readRDS(file = here::here("models/first_model.rds"))
```

@@

# modelsummary::modelsummary(
#   list(
#     "First model" = first_model
#   ),
#   statistic = "mad",
#   fmt = 2
# )
```

@@

# pp_check(first_model) +
#   theme_classic() +
#   theme(legend.position = "bottom")
# 
# posterior_vs_prior(first_model) +
#   theme_minimal() +
#   scale_color_brewer(palette = "Set1") +
#   theme(legend.position = "bottom") +
#   coord_flip()
```

@@

# plot(first_model, "trace")
# 
# plot(first_model, "rhat")
```

>>>>

library(arrow)
library(knitr)
library(kableExtra)
library(modelsummary)
library(rstanarm)
library(tidyverse)
library(ggplot2)
library(bayesplot)
library(broom)
```

@@

# Load in data
cleaned_aerial_priority <- read_parquet(here::here("data/analysis_data/cleaned_aerial_priority.parquet"))

# Random sampling if needed
set.seed(302)
sampled_data <- cleaned_aerial_priority %>%
  sample_n(3000)

# ces2022_1 |>
#   head() |>
#   kable(
#     col.names = c("Voted For (2020)", "Age Group", "Gender", "Education", "Race", "Religion"),
#     booktabs = TRUE
  # )
```

@@

# Load in models
aerial_priority_model <-
  readRDS(file = here::here("models/aerial_priority_model.rds"))
```

@@

# Print the summary of the model to inspect the results
print(summary(aerial_priority_model))

# Optional: Plot the effects to visualize the model results
plot(aerial_priority_model)

prior_summary(aerial_priority_model)

@@

pp_check(aerial_priority_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(aerial_priority_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(aerial_priority_model, "trace")

plot(aerial_priority_model, "rhat")
```
